Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-04 WSSSPE1_report/WSSSPE1_summary_report.tex
moving licensing from cross-cutting to note in conclusions
small updates in process section

A peer review process followed the submissions, where the 58 papers received 181 reviews, an 
average of 3.12 reviews per paper. Reviews were completed using a Google form, which allowed 
reviewers to provide scores on relevance and comments to the organizers and to the authors. The review reports enabled the organizers to decide which papers to associate with the workshop, and the authors to improve their papers.

@@

\section{Cross-cutting Issues}  \label{sec:cross-cutting}

\subsection{Defining sustainability}

@@

\subsection{Licensing}

\note{not sure if this was really cross-cutting...}

@@

>>>>

A peer review process followed the submissions, where the 58 papers received 181 reviews, an 
average of 3.12 reviews per paper. Reviews were completed using a Google form, which allowed 
reviewers to choose papers they wanted to review, then to provide scores on their relevance and general comments to the organizers and to the authors. The review reports enabled the organizers to decide which papers to associate with the workshop, and allowed the authors to improve their papers.

@@

\section{Cross-cutting Issue: Defining Sustainability}  \label{sec:cross-cutting}

@@

@@

\todo{say something about licensing - lessons, advice, etc.?}
